---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# calcalr

**WORK in PROGRESS**

<!-- badges: start -->
<!-- badges: end -->

The calcalr package implements the algorithms of the book

> E. M. Reingold, N. Dershowitz "_Calendrical Calculations - The Ultimate Edition_",
> Cambridge University Press, April 2018

## Concepts

The easiest way to reckon time is simply to count days.
Reingold and Dershowitz have chosen midnight at the onset of Monday, January 1, 1 (Gregorian) as
the fixed date 1, which is abbreviate as R.D.[^1] 1.

[^1]: R.D. stands for *Rata Die*, or fixed date in Latin.

An R.D. that has a fractional part giving the time of day is called a “*moment*”.
So noon on day *i* would be specified by $i + 0.5$.


All calendars provide conversion functions to/from R.D. making it possible to convert
from any one calendar to any other one.

## Installation

You can install the development version of calcalr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("espinielli/calcalr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# library(calcalr)
## basic example code
```

